---
title: "Group Project"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---


# Question 1: Is there a heightened risk of mortality associated with alcohol consumption?
```{r}
```
# Question 2: Among different age groups (children, adults, and senior citizens), which demographic exhibits the highest mortality rate?
```{r}
```
# Question 3: Can the presence of medical conditions like diabetes, hepatic failure, or other medical conditions impact an individual's likelihood of mortality?
```{r}
```
# Question 4: What is the gender distribution of deaths in the hospital, with regard to male and female ratios? 
```{r}
```
# Question 5: Is there a heightened risk of mortality associated with alcohol consumption?
```{r}
```
# Question 6: Among different age groups (children, adults, and senior citizens), which demographic exhibits the highest mortality rate?

```{r}
```
# Question 7: Can the presence of medical conditions like diabetes, hepatic failure, or other medical conditions impact an individual's likelihood of mortality?
```{r}
```